\speculake: Hiding Malware in Speculative Execution

### 2018-05-07 paper/implementation.tex
section intro

\section{Implementation and Evaluation}

>>>>

\section{Implementation and Evaluation}
We now discuss the details of our implementations and the information learned
about speculative execution gained by these experiments. We discuss how we gain
confidence in information passed back, and how a low number of iterations is
sufficient to gain a strong confidence in results.
